The Unified Nature of the Dielectric Properties of Two-Dimensional Materials

### 2018-11-15 paper.tex
Correct minor grammatic errors

\author{Tian Tian}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\altaffiliation{T. T. and D. S. contributed equally to this work}
\author{Declan Scullion}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\altaffiliation{T. T. and D. S. contributed equally to this work}
\author{Dale Hughes}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\author{Lu Hua Li}
\affiliation{Institute for Frontier Materials, Deakin University, Waurn Ponds, Victoria, Australia}
\author{Chih-Jen Shih}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\author{Jonathan Coleman}
\affiliation{School of Physics, Centre for Research on Adaptive Nanostructures and Nanodevices (CRANN) and Advanced Materials and BioEngineering Research (AMBER), Trinity College Dublin, Dublin 2, Ireland.}
\author{Manish Chhowalla}
% \affiliation{Materials Science and Engineering, Rutgers University, 607 Taylor Road, Piscataway, New Jersey 08854, USA.}
\affiliation{Department of Materials Science \& Metallurgy, University of Cambridge, CB3 0FS, United Kindom}
\author{Elton J. G. Santos}
\email{e.santos@qub.ac.uk}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\date{}
\title{The Unified Nature of the Dielectric Properties of Two-Dimensional Materials}
% \title{Unified Understanding of the Dielectric Nature of Two-Dimensional Materials}
\begin{document}

@@

from the its bandgap with with a reasonable degree of certainty

@@

\varepsilon_{\mathrm{SL}}^{zz}$. The absense of bonding perpendicular

@@

respectivel, the model-predicted

@@

\subsection{2D Moss-like  Relations}
\label{sec:first-principles}
Based on the 2D polarizabilities, we then investigate the potential
Moss-like relations for 2D materials. By evaluating the expressions
for $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$ using Random Phase Approximation (RPA)
theory \cite{Adler_1962} with $\mathbf{k} \cdot \mathbf{p}$
treatment\cite{kittel_2005_introduction} (details see Supplementary
Section \ref{SI-ssec:theory-1}), we show that
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
have simple relation with the electronic  and structural information of a 2D
material, respectively:
\begin{subequations}
\begin{eqnarray}
\label{eq:2D-Moss-para}
  &\alpha_{\mathrm{2D}}^{\parallel} &\propto E_{g}^{-1} \\
  \label{eq:2D-Moss-perp}
  &\alpha_{\mathrm{2D}}^{\perp} & \propto \delta
\end{eqnarray}
\end{subequations}
where $E_{\mathrm{g}}$ is the minimal electronic bandgap of the 2D
material, and $\delta$ is its intrinsic
thickness. Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} are
the main conclusions of this work.  \todo[inline]{I not sure if we
  need to show the proportional coefficiens
  here. $\alpha_{2D}^{\perp}$ is almost certain to be
  $\varepsilon_{0}\delta$, but $\alpha_{\mathrm{2D}}^{\parallel}$ has
  a more complex coefficient.}

To validate such relations, we study several types of 2D materials as
show in Figure \ref{fig-3}a, including transition metal
dichalcogenides (TMDCs, with the formula MX\(_{\text{2}}\), where M is
a metal in group 4, 6, 10 and X=O, S, Se, Te), metal monochalcogenides
(Ga$_{2}$S$_{2}$, Ga$_{2}$Se$_{2}$), cadmium halides (CdX$_2$, X=Cl,
I), hexagonal boron nitride (BN), graphene derivatives (fluorographene
(C$_{2}$F$_{2}$), graphane (C$_{2}$H$_{2}$)), phosphorene (P$_{4}$)
and thin layer organic-inorganic perovskites (ABX$_{3}$).  For the
TMDCs, we consider 2 lattice phases, namely the 2H (P\(\bar{6}\)m2
space group) and 1T (P3m1 space group).  The static 2D
polarizabilities are calculated from the static dielectric response of
the selected 2D materials using density functional theory (DFT) with
the Heyd-Scuseria-Ernzerhof hybrid functionals (HSE06) using the
Vienna Ab Initio Simulation Package (VASP) including spin-orbit
coupling to avoid limitations on the description of band gaps and
dielectric functions (see Methods for details). Figure \ref{fig-3}b
shows the calculated $E_{\mathrm{g}}$ (blue dots) and polarizabilities
(bar plots) of all the 2D materials investigated, covering a wide
spectrum range from far infrared to ultraviolet. Note from dimension
analysis, it is more intuitive to express the polarizability as
$\alpha_{\mathrm{2D}}/(4 \pi \varepsilon_{0})$, which has unit of
\AA. We find that $\alpha_{\mathrm{2D}}^{\parallel}$ has a general
descending trend when $E_{\mathrm{g}}$ increases. On the other hand,
no apparent correlation between $\alpha_{\mathrm{2D}}^{\perp}$ and
$E_{\mathrm{g}}$ is observed (see Supplementary Section
\ref{SI-sec:pol-2D-Eg}), which appears to be in good agreement with
our polarizability-based theoretical model (Supplementary Section
\ref{SI-ssec:theory-2}). We then examine Eqs. \ref{eq:2D-Moss-para}
and \ref{eq:2D-Moss-perp} using the polarizabilities calculated by
first principle calculations. Figure \ref{fig-3}b shows
$(4 \pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ (in
\AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$ (in eV) for the 2D
materials investiaged (circle dots), with a linear regression
coefficient of regression $R^{2}$ of 0.84, and a slope of 0.18, which
corresponds well with theoretical investigations (details see
Supplementary Section \ref{SI-sssec:theory-1}).  We also discover that
the linearity between
$(4 \pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ and
$E_{\mathrm{g}}$ (measured by the $R^{2}$ value) is higher when the
bandgap is calculated using the HSE06 hybrid functionals, compared
with that from the Perdew--Burk--Ernzerhof (PBE) exchange correlations
(details see Supplementary Section \ref{SI-sec:pol-2D-Eg} and
Supplementary Figure \ref{SI-fig:alpha-Eg-diff}), which can be
explained by the fact that the electronic structure, in particular the
bandgap, is generally better predicted at HSE06 level than PBE level
\cite{Heyd_2005}. It should be noted that although even more accurate
estimation of both dielectric properties and bandgap can be achieved
via many-body Green’s function method (GW) together with the
Bethe-Salpeter equation (BSE), the convergence of such method is known
to be highly affected by the dielectric screening of 2D materials
\cite{Hueser_2013_2Dvs3D}. Combining the accuracy, computational
effort and convergence, the choice of the HSE06 hybrid functional may
be most suitable to present the true 2D Moss-like relationship between
$\alpha_{\mathrm{2D}}^{\parallel}$ and $E_{\mathrm{g}}$. We also show
that the proposed relation behaves equivalently well when using the
experimentally accessible optical bandgap of 2D materials (details see
Supplementary Section \ref{SI-sec:gpaw-2} and Supplementary Figure
\ref{SI-fig:opt}).

@@

To rule out the possibility that our conclusion is limited by the
number of materials used, we further validate our proposed 2D
Moss-like relations on the recently-published C2DB database
\cite{Haastrup_2018}, from which we extracted the dielectric
properties of over 230 2D materials calculated at the PBE level, and
superimpose with our results in Figure \ref{fig-3}b and \ref{fig-3}c
(details see Supplementary Section \ref{SI-sec:gpaw-1}). Althought the
dielectric properties may be overestimated at PBE level due to
underestimation of the bandgap compared with the more accurate HSE06
functionals \cite{Van_Dyck_2017}, similar linear trends can be
observed for both $\alpha^{\parallel}_{\mathrm{2D}}$ and
$\alpha_{\mathrm{2D}}^{\perp}$, with the linear coefficient very close
to the HSE06 results (details see Supplementary Section
\ref{SI-sec:gpaw-2}). We have also tested the potential relation
between the 2D polarizabilities with other physical quantities,
including the effective carrier mass, quantum capacitance and total
atomic polarizabilities, while no apparent correlations are found
(details see Supplementary Section \ref{SI-sec:gpaw-3}).

In short, we have revealed the 2D analog of the Moss relation by both
theoretical modeling and first principles calculations:
$\alpha_{\mathrm{2D}}^{\parallel}$ is inversely proportional to the
minimal bandgap $E_{\mathrm{g}}$, while $\alpha_{\mathrm{2D}}^{\perp}$
is the characteristic thickness of the 2D material. Next we show,
despite their different forms, both 2D Moss-like relations stem from
the same origin. In merit of the unit analysis,
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
both have unit of $4\pi\varepsilon_{0} \cdot$[Length], or in other
words, $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$ correspond to in- and out-of-plane
characteristic lengthes, respectively. The in-plane screened
electrostatic potential $V(r)$ from a point charge in an 2D plane, as
a function of distance $r$:
$V(r) = {\displaystyle \frac{e}{4 \alpha_{\mathrm{2D}}^{\parallel}}}
\left[H_{0}({\displaystyle \frac{2\varepsilon_{0}
      r}{\alpha_{\mathrm{2D}}^{\parallel}}}) - Y_{0}( {\displaystyle
    \frac{2
      \varepsilon_{0}r}{\alpha_{\mathrm{2D}}^{\parallel}}})\right]$
\cite{Keldysh_1979_eps_multi,Pulci_2014}, where $H_{0}$ is the Struve
function and $Y_{0}$ is the Bessel function of second kind, is
associated with the in-plane screening radius
$r_{0}^{\parallel}=\alpha_{\mathrm{2D}}^{\parallel}/(2
\varepsilon_{0})$, such that $V(r,r/r^{\parallel}_{0} \gg 1)$ reduces
to the simple Coulombic potential in vacuum. Combining with the result
that $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ characterizes the
thickness of a 2D material, we have drawn a generalized picture of the
dielectric nature of 2D materials via the 2D polarizability: the
dielectric screening of a point charge sitting in the middle of a 2D
material can be viewed as an ellipsoid with the length of principle
axes to be
$r_{0}^{\parallel} = \alpha_{\mathrm{2D}}^{\parallel}/(2
\varepsilon_{0})$ and
$r_{0}^{\perp} = \alpha^{\perp}_{\mathrm{2D}}/(2 \varepsilon_{0})$,
respectively, analog to the polarizability ellipsoid picture of
molecules used in spectroscopy \cite{Banwell_1994} (see Supplementary
Figure \ref{SI-fig:ellipsoid}). The polarizability ellipsoid for a 2D
material is in general ultra flat, with
$r_{0}^{\parallel} \gg r_{0}^{\perp}$, as can be seen from the group 6
TMDCs in Table \ref{tbl:radii}\todo{Lacks MoSe2}.  Moreover,
$r_{0}^{\parallel}$ is generally larger for a smaller bandgap
semiconductor, which qualitatively explains the inverse propotional
relation between $\alpha_{\mathrm{2D}}^{\parallel}$ and
$E_{\mathrm{g}}$, a 2D version of the Moss-relation.

@@

The universal Moss-like relation shown in the previous sections
provides general understanding of the dielectric nature of 2D
materials. Moreover, the underlying physical mechanism allows us to
further bridge the 2D and 3D dielectric and electronic properties in
various ways. Using the similar appraoch as we derive the 2D Moss-like
relations, we show that the
$\alpha_{\mathrm{2D}}^{\parallel} \propto E_{\mathrm{g}}^{-1}$
relation for a 2D material naturally transforms to
$\varepsilon \propto E_{\mathrm{g}}^{-\frac{1}{2}}$ for a bulk
semiconductor, which is the original Moss relation (details see
Supplementary Section \ref{SI-ssec:theory-2}). In other words, the
proposed $\alpha_{\mathrm{2D}}^{\parallel}-E_{\mathrm{g}}$ relation is
indeed the Moss relation in 2D world, while the different power law
for $E_{\mathrm{g}}$ is caused by the electronic confinement.
\todo[inline]{I shortened this paragraph since the derivation is
  interesting but not so much related with other stuff like the
  dielectric anisotropy.}

The dielectric constant $\varepsilon$, although not well-defined for
monolayer 2D material, becomes applicable when the 2D layers are
stacked. \todo[inline]{I would appreciate for polishing this sentence}
In a bulk layered materil stacked by layers with equilibrium
inter-layer distance $L_{\mathrm{Bulk}}$, we define the polarizability
of individual layer $\alpha_{\mathrm{2D}}(L=L_{\mathrm{Bulk}})$ as
$\alpha_{\mathrm{Bulk}}$. Inspired by Eqs. \ref{eq:alpha-para-def} and
\ref{eq:alpha-perp-def}, the dielectric constants
$\varepsilon^{\parallel}_{\mathrm{Bulk}}$ and
$\varepsilon^{\perp}_{\mathrm{Bulk}}$ of a bulk layered material, can
be reconstructed by $\alpha_{\mathrm{Bulk}}^{\parallel}$ and
$\alpha_{\mathrm{Bulk}}^{\perp}$ (see Figure \ref{fig-4}a):
\begin{subequations}
\begin{align}
  \label{eq:3D-para}
  \varepsilon^{\parallel}_{\mathrm{Bulk}}
  &= 1 + \frac{\alpha_{\mathrm{bulk}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{Bulk}}}
  \approx 1 + \frac{\alpha_{\mathrm{2D}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{Bulk}}} \\
  \label{eq:3D-perp}
  \varepsilon^{\perp}_{\mathrm{Bulk}}
  &= \left(1 - \frac{\alpha_{\mathrm{Bulk}}^{\perp}}{\varepsilon_{0} L_{\mathrm{Bulk}}}\right)^{-1}
  \approx \left(1 - \frac{\alpha_{\mathrm{2D}}^{\perp}}{\varepsilon_{0} L_{\mathrm{Bulk}}}\right)^{-1}
\end{align}
\end{subequations}
The approximations come from the fact that
$\alpha_{\mathrm{Bulk}} \approx \alpha_{\mathrm{2D}}$, which can be
seen from the results of Figure \ref{fig-3}b and \ref{fig-3}c.  Note
that the effect of stacking is not considered in Eqs. \ref{eq:3D-para}
and \ref{eq:3D-perp}. We compare the values of
$\varepsilon_{\mathrm{bulk}}^{\parallel}$ and
$\varepsilon_{\mathrm{bulk}}^{\perp}$ from DFT calculations (y-axis)
with those predicted using Eqs \ref{eq:3D-para} and \ref{eq:3D-perp}
(x-axis), as show in Figure \ref{fig-4}b and \ref{fig-4}c,
respectively, with data calculated at both HSE06 and PBE levels give
almost identical trends. We observe that
$\varepsilon_{\mathrm{bulk}}^{\parallel}$ values calculated by DFT and
predicted by Eq. \ref{eq:3D-para} are in good agreement, with a linear
regression slope of 1.01 and $R^2$ of 0.97. On the other hand,
$\varepsilon_{\mathrm{bulk}}^{\perp}$ values predicted from
Eq. \ref{eq:3D-perp} agree well with the DFT-calculated values when
$E_{\mathrm{g}}>4$ eV, while the deviation becomes larger when
$E_{\mathrm{g}}$ reduces. The above results indicate that
$\alpha^{\parallel}_{\mathrm{Bulk}}$ can generally be estimated from
its 2D counterpart, while $\alpha^{\perp}_{\mathrm{Bulk}}$ differs due
to interlayout coupling and overlap between induced
dipoles\cite{Andersen_2015_dielec_vdWH,Laturia_2018}, as also observed
in Figure \ref{fig-3}b, \ref{fig-3}c . With a better model describing
$\alpha_{\mathrm{bulk}}^{\perp}$ as function of $\alpha_{\mathrm{2D}}^{\perp}$ and
the degree of interlayer coupling, the dielectric transition from 2D
to 3D would be smoothly described.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.95\linewidth]{img/fig5.pdf}
  \caption{\textbf{Phase diagram of dielectric anisotropy $\eta$ as
      function of bandgap $E_{\mathrm{g}}$}. The
    $\eta$-$E_{\mathrm{g}}$ values of 2D materials (blue triangle) and
    their bulk counterparts (orange square) can be distinguished by
    the line $y=0.048x+0.087$. $\eta-E_{\mathrm{g}}$ values of
    semiconducting materials in other dimensions are also superimposed
    for comparison. Isotropic dielectric property is observed for bulk
    covalent materials (3D, red triangle) and fullerenes (0D, green
    star), while reduced dimensional materials, including planar
    organic semiconductor(OSc, 1D-2D, brown triangle), carbon nanotube
    (CNT, magenta circle) and linear OSc (0D-1D, violet pentagon) are
    scattered along the boundary line. The dimensionality and
    structure of typical materials are shown along the axis on the
    right. Compared with other materials, 2D materials and their bulk
    counterparts provide more flexibility of controlling the
    dielectric anisotropy.}
  \label{fig:aniso}
\end{figure}

>>>>

\author{Tian Tian}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\altaffiliation{T. T. and D. S. contributed equally to this work}
\author{Declan Scullion}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\altaffiliation{T. T. and D. S. contributed equally to this work}
\author{Dale Hughes}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\author{Lu Hua Li}
\affiliation{Institute for Frontier Materials, Deakin University, Waurn Ponds, Victoria, Australia}
\author{Chih-Jen Shih}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\author{Jonathan Coleman}
\affiliation{School of Physics, Centre for Research on Adaptive Nanostructures and Nanodevices (CRANN) and Advanced Materials and BioEngineering Research (AMBER), Trinity College Dublin, Dublin 2, Ireland.}
\author{Manish Chhowalla}
% \affiliation{Materials Science and Engineering, Rutgers University, 607 Taylor Road, Piscataway, New Jersey 08854, USA.}
\affiliation{Department of Materials Science \& Metallurgy, University of Cambridge, CB3 0FS, United Kingdom}
\author{Elton J. G. Santos}
\email{e.santos@qub.ac.uk}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\date{}
\title{The Unified Nature of the Dielectric Properties of Two-Dimensional Materials}
% \title{Unified Understanding of the Dielectric Nature of Two-Dimensional Materials}
\begin{document}

@@

from the its bandgap with a reasonable degree of certainty

@@

\varepsilon_{\mathrm{SL}}^{zz}$. The absence of bonding perpendicular

@@

respectively, the model-predicted

@@

\subsection{2D Moss-like  Relations}
\label{sec:first-principles}
Based on the 2D polarizabilities, we then investigate the potential
Moss-like relations for 2D materials. By evaluating the expressions
for $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$ using Random Phase Approximation (RPA)
theory \cite{Adler_1962} with $\mathbf{k} \cdot \mathbf{p}$
treatment\cite{kittel_2005_introduction} (details see Supplementary
Section \ref{SI-ssec:theory-1}), we show that
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
have simple relation with the electronic  and structural information of a 2D
material, respectively:
\begin{subequations}
\begin{eqnarray}
\label{eq:2D-Moss-para}
  &\alpha_{\mathrm{2D}}^{\parallel} &\propto E_{g}^{-1} \\
  \label{eq:2D-Moss-perp}
  &\alpha_{\mathrm{2D}}^{\perp} & \propto \delta
\end{eqnarray}
\end{subequations}
where $E_{\mathrm{g}}$ is the minimal electronic bandgap of the 2D
material, and $\delta$ is its intrinsic
thickness. Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} are
the main conclusions of this work.  \todo[inline]{I not sure if we
  need to show the proportional coefficients
  here. $\alpha_{2D}^{\perp}$ is almost certain to be
  $\varepsilon_{0}\delta$, but $\alpha_{\mathrm{2D}}^{\parallel}$ has
  a more complex coefficient.}

To validate such relations, we study several types of 2D materials as
show in Figure \ref{fig-3}a, including transition metal
dichalcogenides (TMDCs, with the formula MX\(_{\text{2}}\), where M is
a metal in groups 4, 6, 10 and X=O, S, Se, Te), metal monochalcogenides
(Ga$_{2}$S$_{2}$, Ga$_{2}$Se$_{2}$), cadmium halides (CdX$_2$, X=Cl,
I), hexagonal boron nitride (BN), graphene derivatives (fluorographene
(C$_{2}$F$_{2}$), graphane (C$_{2}$H$_{2}$)), phosphorene (P$_{4}$)
and thin layer organic-inorganic perovskites (ABX$_{3}$).  For the
TMDCs, we consider 2 lattice phases, namely the 2H (P\(\bar{6}\)m2
space group) and 1T (P3m1 space group).  The static 2D
polarizabilities are calculated from the static dielectric response of
the selected 2D materials using density functional theory (DFT) with
the Heyd-Scuseria-Ernzerhof hybrid functionals (HSE06) using the
Vienna Ab Initio Simulation Package (VASP) including spin-orbit
coupling to avoid limitations on the description of band gaps and
dielectric functions (see Methods for details). Figure \ref{fig-3}b
shows the calculated $E_{\mathrm{g}}$ (blue dots) and polarizabilities
(bar plots) of all the 2D materials investigated, covering a wide
spectrum range from far infrared to ultraviolet. Note from dimension
analysis, it is more intuitive to express the polarizability as
$\alpha_{\mathrm{2D}}/(4 \pi \varepsilon_{0})$, which has unit of
\AA. We find that $\alpha_{\mathrm{2D}}^{\parallel}$ has a general
descending trend when $E_{\mathrm{g}}$ increases. On the other hand,
no apparent correlation between $\alpha_{\mathrm{2D}}^{\perp}$ and
$E_{\mathrm{g}}$ is observed (see Supplementary Section
\ref{SI-sec:pol-2D-Eg}), which appears to be in good agreement with
our polarizability-based theoretical model (Supplementary Section
\ref{SI-ssec:theory-2}). We then examine Eqs. \ref{eq:2D-Moss-para}
and \ref{eq:2D-Moss-perp} using the polarizabilities calculated by
first principle calculations. Figure \ref{fig-3}b shows
$(4 \pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ (in
\AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$ (in eV) for the 2D
materials investigated (circle dots), with a linear regression
coefficient of regression $R^{2}$ of 0.84, and a slope of 0.18, which
corresponds well with theoretical investigations (details see
Supplementary Section \ref{SI-sssec:theory-1}).  We also discover that
the linearity between
$(4 \pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ and
$E_{\mathrm{g}}$ (measured by the $R^{2}$ value) is higher when the
bandgap is calculated using the HSE06 hybrid functionals, compared
with that from the Perdew--Burk--Ernzerhof (PBE) exchange correlations
(details see Supplementary Section \ref{SI-sec:pol-2D-Eg} and
Supplementary Figure \ref{SI-fig:alpha-Eg-diff}), which can be
explained by the fact that the electronic structure, in particular the
bandgap, is generally better predicted at HSE06 level than PBE level
\cite{Heyd_2005}. It should be noted that although even more accurate
estimation of both dielectric properties and bandgap can be achieved
via many-body Green's function method (GW) together with the
Bethe-Salpeter equation (BSE), the convergence of such method is known
to be highly affected by the dielectric screening of 2D materials
\cite{Hueser_2013_2Dvs3D}. Combining the accuracy, computational
effort and convergence, the choice of the HSE06 hybrid functional may
be most suitable to present the true 2D Moss-like relationship between
$\alpha_{\mathrm{2D}}^{\parallel}$ and $E_{\mathrm{g}}$. We also show
that the proposed relation behaves equivalently well when using the
experimentally accessible optical bandgap of 2D materials (details see
Supplementary Section \ref{SI-sec:gpaw-2} and Supplementary Figure
\ref{SI-fig:opt}).

@@

To rule out the possibility that our conclusion is limited by the
number of materials used, we further validate our proposed 2D
Moss-like relations on the recently published C2DB database
\cite{Haastrup_2018}, from which we extracted the dielectric
properties of over 230 2D materials calculated at the PBE level, and
superimpose with our results in Figure \ref{fig-3}b and \ref{fig-3}c
(details see Supplementary Section \ref{SI-sec:gpaw-1}). Although the
dielectric properties may be overestimated at PBE level due to
underestimation of the bandgap compared with the more accurate HSE06
functionals \cite{Van_Dyck_2017}, similar linear trends can be
observed for both $\alpha^{\parallel}_{\mathrm{2D}}$ and
$\alpha_{\mathrm{2D}}^{\perp}$, with the linear coefficient very close
to the HSE06 results (details see Supplementary Section
\ref{SI-sec:gpaw-2}). We have also tested the potential relation
between the 2D polarizabilities with other physical quantities,
including the effective carrier mass, quantum capacitance and total
atomic polarizabilities, while no apparent correlations are found
(details see Supplementary Section \ref{SI-sec:gpaw-3}).

In short, we have revealed the 2D analog of the Moss relation by both
theoretical modeling and first principles calculations:
$\alpha_{\mathrm{2D}}^{\parallel}$ is inversely proportional to the
minimal bandgap $E_{\mathrm{g}}$, while $\alpha_{\mathrm{2D}}^{\perp}$
is the characteristic thickness of the 2D material. Next we show,
despite their different forms, both 2D Moss-like relations stem from
the same origin. In merit of the unit analysis,
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
both have unit of $4\pi\varepsilon_{0} \cdot$[Length], or in other
words, $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$ correspond to in- and out-of-plane
characteristic lengths, respectively. The in-plane screened
electrostatic potential $V(r)$ from a point charge in an 2D plane, as
a function of distance $r$:
$V(r) = {\displaystyle \frac{e}{4 \alpha_{\mathrm{2D}}^{\parallel}}}
\left[H_{0}({\displaystyle \frac{2\varepsilon_{0}
      r}{\alpha_{\mathrm{2D}}^{\parallel}}}) - Y_{0}( {\displaystyle
    \frac{2
      \varepsilon_{0}r}{\alpha_{\mathrm{2D}}^{\parallel}}})\right]$
\cite{Keldysh_1979_eps_multi,Pulci_2014}, where $H_{0}$ is the Struve
function and $Y_{0}$ is the Bessel function of second kind, is
associated with the in-plane screening radius
$r_{0}^{\parallel}=\alpha_{\mathrm{2D}}^{\parallel}/(2
\varepsilon_{0})$, such that $V(r,r/r^{\parallel}_{0} \gg 1)$ reduces
to the simple Coulomb potential in vacuum. Combining with the result
that $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ characterizes the
thickness of a 2D material, we have drawn a generalized picture of the
dielectric nature of 2D materials via the 2D polarizability: the
dielectric screening of a point charge sitting in the middle of a 2D
material can be viewed as an ellipsoid with the length of principle
axes to be
$r_{0}^{\parallel} = \alpha_{\mathrm{2D}}^{\parallel}/(2
\varepsilon_{0})$ and
$r_{0}^{\perp} = \alpha^{\perp}_{\mathrm{2D}}/(2 \varepsilon_{0})$,
respectively, analog to the polarizability ellipsoid picture of
molecules used in spectroscopy \cite{Banwell_1994} (see Supplementary
Figure \ref{SI-fig:ellipsoid}). The polarizability ellipsoid for a 2D
material is in general ultra flat, with
$r_{0}^{\parallel} \gg r_{0}^{\perp}$, as can be seen from the group 6
TMDCs in Table \ref{tbl:radii}\todo{Lacks MoSe2}.  Moreover,
$r_{0}^{\parallel}$ is generally larger for a smaller bandgap
semiconductor, which qualitatively explains the inverse proportional
relation between $\alpha_{\mathrm{2D}}^{\parallel}$ and
$E_{\mathrm{g}}$, a 2D version of the Moss-relation.

@@

The universal Moss-like relation shown in the previous sections
provides general understanding of the dielectric nature of 2D
materials. Moreover, the underlying physical mechanism allows us to
further bridge the 2D and 3D dielectric and electronic properties in
various ways. Using the similar approach as we derive the 2D Moss-like
relations, we show that the
$\alpha_{\mathrm{2D}}^{\parallel} \propto E_{\mathrm{g}}^{-1}$
relation for a 2D material naturally transforms to
$\varepsilon \propto E_{\mathrm{g}}^{-\frac{1}{2}}$ for a bulk
semiconductor, which is the original Moss relation (details see
Supplementary Section \ref{SI-ssec:theory-2}). In other words, the
proposed $\alpha_{\mathrm{2D}}^{\parallel}-E_{\mathrm{g}}$ relation is
indeed the Moss relation in 2D world, while the different power law
for $E_{\mathrm{g}}$ is caused by the electronic confinement.
\todo[inline]{I shortened this paragraph since the derivation is
  interesting but not so much related with other stuff like the
  dielectric anisotropy.}

The dielectric constant $\varepsilon$, although not well-defined for
monolayer 2D material, becomes applicable when the 2D layers are
stacked. \todo[inline]{I would appreciate for polishing this sentence}
In a bulk layered material stacked by layers with equilibrium
inter-layer distance $L_{\mathrm{Bulk}}$, we define the polarizability
of individual layer $\alpha_{\mathrm{2D}}(L=L_{\mathrm{Bulk}})$ as
$\alpha_{\mathrm{Bulk}}$. Inspired by Eqs. \ref{eq:alpha-para-def} and
\ref{eq:alpha-perp-def}, the dielectric constants
$\varepsilon^{\parallel}_{\mathrm{Bulk}}$ and
$\varepsilon^{\perp}_{\mathrm{Bulk}}$ of a bulk layered material, can
be reconstructed by $\alpha_{\mathrm{Bulk}}^{\parallel}$ and
$\alpha_{\mathrm{Bulk}}^{\perp}$ (see Figure \ref{fig-4}a):
\begin{subequations}
\begin{align}
  \label{eq:3D-para}
  \varepsilon^{\parallel}_{\mathrm{Bulk}}
  &= 1 + \frac{\alpha_{\mathrm{bulk}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{Bulk}}}
  \approx 1 + \frac{\alpha_{\mathrm{2D}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{Bulk}}} \\
  \label{eq:3D-perp}
  \varepsilon^{\perp}_{\mathrm{Bulk}}
  &= \left(1 - \frac{\alpha_{\mathrm{Bulk}}^{\perp}}{\varepsilon_{0} L_{\mathrm{Bulk}}}\right)^{-1}
  \approx \left(1 - \frac{\alpha_{\mathrm{2D}}^{\perp}}{\varepsilon_{0} L_{\mathrm{Bulk}}}\right)^{-1}
\end{align}
\end{subequations}
The approximations come from the fact that
$\alpha_{\mathrm{Bulk}} \approx \alpha_{\mathrm{2D}}$, which can be
seen from the results of Figure \ref{fig-3}b and \ref{fig-3}c.  Note
that the effect of stacking is not considered in Eqs. \ref{eq:3D-para}
and \ref{eq:3D-perp}. We compare the values of
$\varepsilon_{\mathrm{bulk}}^{\parallel}$ and
$\varepsilon_{\mathrm{bulk}}^{\perp}$ from DFT calculations (y-axis)
with those predicted using Eqs \ref{eq:3D-para} and \ref{eq:3D-perp}
(x-axis), as show in Figure \ref{fig-4}b and \ref{fig-4}c,
respectively, with data calculated at both HSE06 and PBE levels give
almost identical trends. We observe that
$\varepsilon_{\mathrm{bulk}}^{\parallel}$ values calculated by DFT and
predicted by Eq. \ref{eq:3D-para} are in good agreement, with a linear
regression slope of 1.01 and $R^2$ of 0.97. On the other hand,
$\varepsilon_{\mathrm{bulk}}^{\perp}$ values predicted from
Eq. \ref{eq:3D-perp} agree well with the DFT-calculated values when
$E_{\mathrm{g}}>4$ eV, while the deviation becomes larger when
$E_{\mathrm{g}}$ reduces. The above results indicate that
$\alpha^{\parallel}_{\mathrm{Bulk}}$ can generally be estimated from
its 2D counterpart, while $\alpha^{\perp}_{\mathrm{Bulk}}$ differs due
to interlayer coupling and overlap between induced
dipoles\cite{Andersen_2015_dielec_vdWH,Laturia_2018}, as also observed
in Figure \ref{fig-3}b, \ref{fig-3}c . With a better model describing
$\alpha_{\mathrm{bulk}}^{\perp}$ as function of $\alpha_{\mathrm{2D}}^{\perp}$ and
the degree of interlayer coupling, the dielectric transition from 2D
to 3D would be smoothly described.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.95\linewidth]{img/fig5.pdf}
  \caption{\textbf{Phase diagram of dielectric anisotropy $\eta$ as
      function of bandgap $E_{\mathrm{g}}$}. The
    $\eta$-$E_{\mathrm{g}}$ values of 2D materials (blue triangle) and
    their bulk counterparts (orange square) can be distinguished by
    the line $\eta=0.048(E_{\mathrm{g}}/\mathrm{eV})+0.087$. $\eta-E_{\mathrm{g}}$ values of
    semiconducting materials in other dimensions are also superimposed
    for comparison. Isotropic dielectric property is observed for bulk
    covalent materials (3D, red triangle) and fullerenes (0D, green
    star), while reduced dimensional materials, including planar
    organic semiconductor(OSc, 1D-2D, brown triangle), carbon nanotube
    (CNT, magenta circle) and linear OSc (0D-1D, violet pentagon) are
    scattered along the boundary line. The dimensionality and
    structure of typical materials are shown along the axis on the
    right. Compared with other materials, 2D materials and their bulk
    counterparts provide more flexibility of controlling the
    dielectric anisotropy.}
  \label{fig:aniso}
\end{figure}
